---
title: "Air quality 2019:Things you should know about Seoul, Republic of Korea"
author: "YJunKim"
date: '2020 7 18 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(pacman)
library(raster)
p_load(flexdashboard, leaflet, rmapshaper, ggplot2, dplyr, tidyr)
setwd("D:/RWORK/BLOG/")
```

## Introduction
블로그 테스트1. 2019년 서울시의 대기질의 살펴보기 위하여 25개 도시 대기측정소 자료를 사용하였다. 대기질을 평가하기 위하여 25개 도시대기측정소를 사용하였다.
This article describes the assessment of air quality around Seoul(Republic of Korea) for the period 2019 based on the data from 25 realtime air quality monitors(see <http://cleanair.seoul.go.kr>. For the assessment, I will be using the PM2.5 (particulate matter of size 2.5 microns or below measured in ug/m3) measurements done by 25 monitors at various locations around Seoul.


```{r cars, echo=FALSE}
stn <- read.csv('station_info_201909.csv')
stn$flag
#pal <- colorFactor("YlOrRd", stn$pm2.5)
leaflet(stn) %>%
  setView(lng=126.9784, lat=37.566, zoom=10) %>%
  addProviderTiles('CartoDB.Positron') %>%
  #addProviderTiles('Stamen.Toner') %>%
  addCircles(data = stn %>% filter(flag == "도시대기"),
              lng=~lon, lat=~lat, popup=~name, group ="도시대기",
              color = "darkred") %>%
  addCircles(data = stn %>% filter(flag == "도로변"),
              lng=~lon, lat=~lat, popup=~name, group ="도로변",
              color = "darkblue") %>%
  addLayersControl(overlayGroups = c("도시대기","도로변"),
                   options = layersControlOptions(collapsed = FALSE))
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
